---
title: "Using extractOz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using_extractOz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding
  %\VignetteDepends{dplyr}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(extractOz)
library(dplyr)
```

## Create locations in WA and NSW

```{r create-location}
locs <- data.frame(
  site = c("Merredin", "Corrigin", "Tamworth"),
  "x" = c(118.28, 117.87, 150.84),
  "y" = c(-31.48, -32.33, -31.07)
)
```

## Extract the GRDC AgroEcological Zones

See `?extract_ae_zone()` for more help on how to use this function.

```{r extract-zones}
z <- extract_ae_zone(x = locs, coords = c("x", "y"))
```

## Extract the soil order

See `?extract_soil_order()` for more help on how to use this function.

```{r extract-soil}
s <- extract_soil_order(x = locs, coords = c("x", "y"))
```

## Get Temperature, Rain and RH for these Locations in 2020

Using the previously created data frame, fetch weather data from SILO for 2020.
This is just an example, replace `MY_EMAIL_ADDRESS` with your email address below.
See `?cropgrowdays::get_multi_silodata()` from for more help on how to use this function.

```{r get-weather, eval=FALSE}
three_sites  <-
  get_multi_silodata(
    latitude = locs$y,
    longitude = locs$x,
    Sitename = locs$site,
    START = "20200101",
    FINISH = "20201231",
    email = MY_EMAIL_ADDRESS
  )
```

## Join the Weather Data with AE Zone, Soil Order and Site Information

Now using `dplyr::left_join()`, create a single `data.frame()` of the Site, GPS coordinates, agroecological zone and weather data.

```{r join, eval=FALSE}
left_join(z, three_sites, by = c("site" = "Sitename")) %>% 
  left_join(s)
```
